I would like to express my deepest gratitude to my advisor, Professor 
    Jéferson Campos Nobre, for his invaluable guidance and expertise throughout 
    my research journey. His patience and profound knowledge have not only 
    shaped this work but have profoundly influenced my development in the field.

    I am immensely thankful to Laura, whose foundational research was 
    instrumental in this thesis. Her dedication and innovative approach have 
    significantly contributed to the success of this project.

    My appreciation also extends to the faculty and staff at the Informatics 
    Department. The education and support provided by the professors have
    been fundamental to my academic and professional growth. Their dedication to
    creating a nurturing and challenging academic environment has been critical 
    to my development.

    Special thanks go to Valéria, my best friend, for her constant support and 
    love. Her encouragement has been a pillar of strength in difficult times, 
    reminding me of the value of perseverance.

    I am grateful to all my friends for their continued encouragement and belief
    in my abilities. Their support and the occasional much-needed distractions 
    have helped me maintain my focus and passion for my research.

    Finally, I would like to thank Marina and Pedro, my psychologist and 
    psychiatrist. Their professional support has been crucial in managing the 
    stress of my academic commitments, significantly contributing to my 
    well-being and success.

    This thesis reflects the collective support and encouragement of everyone 
    mentioned, and I am deeply thankful to each of you.